% hidelinks
% \documentclass[12pt,a4paper,twoside,openright]{scrreprt}
\documentclass[12pt,a4paper,twoside,openright]{report}

% basics
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{cmap} % allow copy paste from pdf
\usepackage{graphicx}
\usepackage{minted}
\usepackage[babel]{microtype}
\usepackage{mathtools}
\usepackage[hyphens]{url}
\usepackage[unicode]{hyperref}
\usepackage[math]{blindtext}
\usepackage[mode=text,group-minimum-digits=4,round-mode=places,round-precision=2]{siunitx}
\usepackage{csquotes}
\usepackage{tikz}
\usetikzlibrary{arrows.meta}

% \usepackage{tabularx}
% \usepackage{listings}
% \usepackage{algorithm}
% \usepackage{algpseudocode}
% \usepackage{amsmath}
% \usepackage{amssymb}
% \usepackage{listingsutf8}
% \usepackage{multirow}
% \usepackage{booktabs}
% \usepackage{longtable}
% \usepackage{float}
% \usepackage{caption}
% \usepackage{abstract}
% \usepackage{ccicons}
% \usepackage{tikz}
% \usepackage{tablefootnote}
% \usepackage{color}
% \usepackage{scrhack}
% \usepackage{array}
% \usepackage{fancyvrb}
% \usepackage{appendix}
% \usepackage[amsmath,hyperref]{ntheorem}

\usepackage[
    title={Implementing a parallel Points-To Analysis},
    author={Lukas Böttcher},
    type={Master Thesis},
    institute={Christian-Albrechts-Universität zu Kiel},
    course={Computer Science},
    examiner={Prof.\ Dr.\ Hans Mustermann},
    supervisor={Dipl.-Inf.\ Roman Tiker,\\Dipl.-Inf.\ Laura Stern,\\Otto Normalverbraucher,\ M.Sc.},
    startdate={2022-08-01},
    enddate={2023-01-16},
    language=english
]{scientific-thesis-cover}

% set up biblatex
\usepackage[
  backend       = biber,
  sortcites     = true,
  bibstyle      = alphabetic,
  citestyle     = alphabetic,
  giveninits    = true,
  useprefix     = false, %"von, van, etc." will be printed, too. See below.
  minnames      = 1,
  minalphanames = 3,
  maxalphanames = 4,
  maxbibnames   = 99,
  maxcitenames  = 2,
  natbib        = true,
  eprint        = true,
  url           = true,
  doi           = true,
  isbn          = true,
  backref       = true]{biblatex}
\bibliography{literatur}

% set up hyperref
\hypersetup{
    linktoc=all,
    bookmarksnumbered=true,
    bookmarksopen=true,
    bookmarksopenlevel=1,
    breaklinks=true,
    pdftitle={Masterarbeit},
    pdfstartview=Fit,
    pdfpagelayout=SinglePage,    
}

\newcommand{\listingautorefname}{listing}

\begin{document}
\pagestyle{empty}
\Coverpage
\Affirmation
\cleardoublepage
\begin{abstract}
    Points-to analysis is a subgroup of static analysis techniques. 
    In general, the goal is to detect a set of memory locations for each pointer element in a program. 
    All major compiler systems make use of this information in order to optimize the given code during compilation
    and most importantly, to detect errors in the program.
    In this thesis an interprocedural inclusion-based pointer analysis, PTAGPU, is presented that utilizes the parallel execution of GPGPUs in order to speedup the analysis as part of the SVF framework. 
    As the SVF framework itself is built on top of the LLVM compiler infrastructure, 
    it is possible to run the proposed analysis on any program that can be compiled inside the LLVM toolchain.
    A meaningful speedup was observed with the proposed parallel implementation compared to the single threaded highly optimized wave propagation inclusion-based analysis.
    An evaluation of the proposed analysis is provided both through the SVF testsuite as well as a collection of open source programs used as benchmarks.
\end{abstract}
\cleardoublepage
\tableofcontents
\cleardoublepage
\listoffigures
\cleardoublepage
\listoftables
\cleardoublepage

\pagestyle{headings}
\input{include/chap1_introduction.tex}
\input{include/chap2_main.tex}
\input{include/chap3_conclusion.tex}
\printbibliography[heading=bibintoc]
\end{document}